Analysing Constraint Grammars with a SAT-solver

### 2016-03-08 paper/lrec/eval_futurework.tex
add GF reference

\clock{} all 
       rules & Xh 12min     & Xh 23min   & Xh 12min &  Xh 4min \\ \hline

@@

\paragraph{Other grammar formalisms}
Finally, we would like to investigate logic-based methods for analysing other grammar
formalisms, for example Grammatical Framework \cite{gf}. (INARI: can you add a reference here?)

>>>>

\clock{} all 
       rules & Xh Ymin     & Xh Ymin   & Xh Ymin &  Xh Ymin \\ \hline

@@

\paragraph{Other grammar formalisms}
Finally, we would like to investigate logic-based methods for analysing other grammar
formalisms, for example Grammatical Framework \cite{ranta2010gfbook}.
